Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-04 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
final intro

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{helvet,times,courier}
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{caption}
\usepackage{todonotes}
\captionsetup[table]{skip=10pt}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

In this work, we suggest a clustering-based method that automatically decomposes a JSP instance into sub-instances which can be tackled by 
optimization algorithms of an ASP solver. 
General clustering algorithms are unsupervised learning methods that partition a given set of objects into disjoint clusters, where each cluster comprises closest objects wrt.\ some distance function. 
In scheduling settings, however, clusters must satisfy additional constraints, which define precedence relations between operations of a job. Standard constrained clustering algorithms are not applicable in scheduling scenarios since they usually allow for the definition of disjointness constraints, which specify objects that cannot appear in one cluster \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. 
%\cite{wagstaff2001constrained}
%where the number of clusters corresponds to the number of sub-problems (windows), and the operations correspond to data objects. For the JSP, an instance consists of a set of jobs to be processed on machines. 
%The number of jobs is $n$, and the number of machines is $m$. Each job contains $m$ operations with the operation precedence constraints. Each operation should be executed on machine $m$ for a certain amount of time. Since the problem at hand has precedence constraints, it is required to apply a constrained clustering approach for the decomposition \cite{wagstaff2001constrained}. Although many studies proposed different constrained clustering methods in \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. However, most of those checked whether two data objects must be assigned into the same cluster. 
Therefore, our clustering method implements a novel type of constraints, which prevent the assignment of an operation to a cluster if its preceding operation is not yet assigned to the same or previous cluster.

It can be said that the attributes of the classical JSP are quite a few and not sufficient to define the similarity and dissimilarity between the operations. The lack of these attributes guides us to extract more features that could specify which operations are similar and should be in the same window and which shall not be in the same window. The main contribution of this work is to extract some features that have a significant impact on the decomposition process and accordingly on the makespan. 
More specifically, we need to extract some features to define which operations are similar to be scheduled in the same window and get a near-optimal solution in a reasonable time. \\

This work consists of two main phases:

\begin{enumerate}
    \item The first phase is to apply data mining to predict the order of each operation on its machine according to some features. In this phase, we will try to get all possible features extracted from the problem itself, which significantly affect the quality of the solution. In addition, we will use some heuristics such as (FIFO, MTWR, EST) to learn the pattern of the solutions obtained by those.

    \item The second phase aims to develop, implement and test a proposed clustering algorithm that will split the problem into sub-problems where each operation is a data object, and each cluster will represent a Time Window (TW). It will consider the precedence constraints between the operations and balancing between the clusters according to the number of operations per cluster.
\end{enumerate}

The paper is organized as follows. The following Section describes the Job-shop Scheduling Problem in detail and shows an illustrative example of input data. Section $3$ shows which features we extracted and how we extracted them, followed by Section $4$, which presents the proposed algorithm. Section $5$ presents an extensive computational study on benchmark instances, comparing our results with the others obtained by some heuristics. A relevant literature review on the subject is given in Section $6$ followed by the conclusion and future work.

@@

\section{Features extraction}
In this section, we show which features have been extracted and how did we extract them. Based on the previous work, \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data}, the following features have been identified: priority, processing time, remaining processing time, machine load, and route position. Most of the researchers converted the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion is to make the decision rules more generic, which can be applied to several scheduling problems. However, in our case, we will not convert the data into classes because we will use these features to measure the similarities/dissimilarities between the operations in the clustering process, which requires having numerical values.
We present the features that we considered:
\subsection{\textit{Process}}
\textit{Processing Time (PT)}  and \textit{Remain Processing Time (RPT)} are attributes dependent on the problem domain. The \textit{PT} represents the execution time of a particular operation in a machine. However, \textit{RPT} is the aggregate processing time for all subsequent operations of that job.

@@

\section{Proposed Algorithm}

In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into TWs because this technique proved its effectiveness for solving the scheduling problems \cite{zhang2010hybrid,zhai2014decomposition}. Several ways have been presented during the last decades to decompose the problem \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\

@@

@@

\section{Literature Review}

In this section, we will review some of the most related works about data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers, and a wide range of approaches has been developed for solving the scheduling problem. One of the approaches that have been widely used to solve the problem is data mining. The main idea of data mining is to explore the patterns from the obtained solutions by some heuristics and then develop some decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of the operations according to some characteristics.\\

@@

\section{Conclusion}
Data mining and machine learning is an area of interest in many manufacturing companies and other fields. In order to increase productivity and decrease the operation cost, there should be high-quality schedules to be used. This study focused on data mining and clustering approaches for solving the Job-shop Scheduling Problem. The first issue in this work is to explore the knowledge in good schedules and try to use this knowledge to get more efficient schedules. We extracted some features from the problem at hand and other features from schedules obtained by heuristics. The second issue is finding a powerful way to decompose the problem into windows where each cluster is a window and solve them sequentially. In order to split the problem, we proposed a constrained clustering algorithm considering the precedence constraints of the JSP. We tested our model on benchmark instances, and the results showed that the performance of the proposed model outperforms other heuristics FIFO, MTWR, and EST in the most cases; and some attributes like (\textit{Starting Time, Waiting Time, Remaining Processing Time, and Machine Load}) played an important role to split the operations in a good way. There are several ways to extend this study. Firstly, solve bigger instances and others in a real-life application in which more features could be extracted. Secondly, develop other clustering algorithms to split the problem more efficiently and get better results.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{helvet,times,courier}
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{caption}
\usepackage{todonotes}
\usepackage[inline]{enumitem}
\captionsetup[table]{skip=10pt}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

In this work, we suggest a clustering-based method that automatically decomposes a JSP instance into sub-instances which can be tackled by 
optimization algorithms of an ASP solver. 
General clustering algorithms are unsupervised learning methods that partition a given set of objects into disjoint clusters, where each cluster comprises closest objects wrt.\ some distance function. 
In scheduling settings, however, clusters must satisfy additional constraints, which define precedence relations between operations of a job. Standard constrained clustering algorithms are not applicable in scheduling scenarios since they usually allow for the definition of disjointness constraints, which specify objects that cannot appear in one cluster \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. 
Therefore, our clustering method implements a novel type of constraints that
\begin{enumerate*}[label=\emph{(\roman*)}]
  \item prevent the assignment of an operation to a cluster if its preceding operation is not yet assigned to the same or previous cluster, and
  \item ensure balancing between the clusters according to the number of operations per cluster.
\end{enumerate*}
Further contributions of this paper can be summarized as follows:
\begin{itemize}
  \item A typical JSP instance describing jobs, their operations, and available machines, does not provide enough information for a clustering algorithm to find a good decomposition. Therefore, we suggest various heuristic feature extractors, such as First-In-First-Out or machine load.
  \item We implement the suggested constrained clustering method and combine it with the forward selection of features. The latter is an automatic procedure aiming to find a subset of features allowing the clustering algorithm to compute a decomposition resulting in the best quality schedule.
  \item Evaluation of our method on the Taillard benchmark instances \cite{taillard1993benchmarks} showed that it significantly outperforms baseline heuristic methods and pure ASP optimization algorithms wrt.\ the makespan optimization criteria within the timeout of 600 seconds.
\end{itemize}
%It can be said that the attributes of the classical JSP are quite a few and not sufficient to define the similarity and dissimilarity between the operations. The lack of these attributes guides us to extract more features that could specify which operations are similar and should be in the same window and which shall not be in the same window. The main contribution of this work is to extract some features that have a significant impact on the decomposition process and accordingly on the makespan. 
%More specifically, we need to extract some features to define which operations are similar to be scheduled in the same window and get a near-optimal solution in a reasonable time. \\

%This work consists of two main phases:

%\begin{enumerate}
%    \item The first phase is to apply data mining to predict the order of each operation on its machine according to some features. In this phase, we will try to get all possible features extracted from the problem itself, which significantly affect the quality of the solution. In addition, we will use some heuristics such as (FIFO, MTWR, EST) to learn the pattern of the solutions obtained by those.

%    \item The second phase aims to develop, implement and test a proposed clustering algorithm that will split the problem into sub-problems where each operation is a data object, and each cluster will represent a Time Window (TW). It will consider the precedence constraints between the operations and balancing between the clusters according to the number of operations per cluster.
%\end{enumerate}

The paper is organized as follows: the following section provides the definition of JSP and gives an illustrative example of input data. Section \ref{sec:features} discusses heuristic feature extractors, followed by Section \ref{sec:method}, which presents the proposed constrained clustering algorithm. Section \ref{sec:eval} presents an extensive computational study on benchmark instances, comparing our results with the baseline solvers. A literature review is given in Section \ref{sec:literature}, followed by the conclusions and future work.

@@

\section{Features extraction}
\label{sec:features}
In this section, we show which features have been extracted and how did we extract them. Based on the previous work, \cite{koonce2000using, harrath2002genetic, shahzad2010discovering, ismail2012production, adibi2014clustering, nasiri2019data}, the following features have been identified: priority, processing time, remaining processing time, machine load, and route position. Most of the researchers converted the attributes into qualitative data. As mentioned in these studies, the main reason for this conversion is to make the decision rules more generic, which can be applied to several scheduling problems. However, in our case, we will not convert the data into classes because we will use these features to measure the similarities/dissimilarities between the operations in the clustering process, which requires having numerical values.
We present the features that we considered:
\subsection{\textit{Process}}
\textit{Processing Time (PT)}  and \textit{Remain Processing Time (RPT)} are attributes dependent on the problem domain. The \textit{PT} represents the execution time of a particular operation in a machine. However, \textit{RPT} is the aggregate processing time for all subsequent operations of that job.

@@

\section{Proposed Algorithm}
\label{sec:method}
In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into TWs because this technique proved its effectiveness for solving the scheduling problems \cite{zhang2010hybrid,zhai2014decomposition}. Several ways have been presented during the last decades to decompose the problem \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\

@@

\label{sec:eval}

@@

\section{Literature Review}
\label{sec:literature}
In this section, we will review some of the most related works about data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers, and a wide range of approaches has been developed for solving the scheduling problem. One of the approaches that have been widely used to solve the problem is data mining. The main idea of data mining is to explore the patterns from the obtained solutions by some heuristics and then develop some decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of the operations according to some characteristics.\\

@@

\section{Conclusions}
\label{sec:conclusions}
Data mining and machine learning is an area of interest in many manufacturing companies and other fields. In order to increase productivity and decrease the operation cost, there should be high-quality schedules to be used. This study focused on data mining and clustering approaches for solving the Job-shop Scheduling Problem. The first issue in this work is to explore the knowledge in good schedules and try to use this knowledge to get more efficient schedules. We extracted some features from the problem at hand and other features from schedules obtained by heuristics. The second issue is finding a powerful way to decompose the problem into windows where each cluster is a window and solve them sequentially. In order to split the problem, we proposed a constrained clustering algorithm considering the precedence constraints of the JSP. We tested our model on benchmark instances, and the results showed that the performance of the proposed model outperforms other heuristics FIFO, MTWR, and EST in the most cases; and some attributes like (\textit{Starting Time, Waiting Time, Remaining Processing Time, and Machine Load}) played an important role to split the operations in a good way. There are several ways to extend this study. Firstly, solve bigger instances and others in a real-life application in which more features could be extracted. Secondly, develop other clustering algorithms to split the problem more efficiently and get better results.
